---
title: "`r params$trip_name`"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "`r Sys.Date()`"
output: word_document
params:
      teams: 4
      days: 3
      file.df: "ErieNiag_2020_9_8_redo.csv"
      trip_name: "Erie_Niag_Screening"
      hab_number_start: 484
      team_1: "Gavin/Keleigh"
      team_2: "Charlie/Jeff"
      team_3: "Meredith/Brian"
      team_4: "Wyndle/Archer"
      print_team: 1
      overnights: TRUE
      hotel_coords: "hotels.csv"
      added_drive_times_day_end: FALSE
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(knitr)
library(flextable)
#insert your file name, number of teams and days here

#file.df<-"ErieNiag_2020_9_8_redo.csv"
#teams<-4
#days<-3
#trip_name<-"ErieNiag_Screening"
#shipping<-data.frame("Location"= c("ALS Courier Service: The ALS address for drop-off is 23A Walker Way, Colonie, The door access code is 6215","Albany,24 Avis Dr, Latham, NY 12110"),"days"=c("Day 2 and 3","Day 1","teams"=))

#hab_number_start<-484


#read in the raw data
file.path=file.path(here::here(),
          "data",
          params$file.df)

file.path.ups=file.path(here::here(),
                        "data",
                        "ups_ont.csv")

sites<-read.csv(file.path,stringsAsFactors = FALSE)

shipping<-read.csv(file.path.ups,stringsAsFactors = FALSE)


#take out the blank ones
sites<-sites %>% 
  subset(!is.na(SH_LATITUDE))

max.sites<-nrow(sites)

```

## Itinerary for Team  `r params$print_team`

This trip has `r max.sites ` sites to visit total.

There are `r params$teams ` teams in this sampling event.
Each team will do `r max.sites/params$teams ` sites over `r params$days `days. So that's `r (max.sites/params$teams)/params$days ` sites per day per team.


1-BLUE: `r params$team_1`     
2-RED: `r params$team_2`  
3-GREEN: `r params$team_3`      
4-PURPLE: `r params$team_4`  


## Types of sites

This is what the site breakdown looks like for the `r params$trip_name ` trip:

```{r,message=FALSE,warning=FALSE}
m.df<-sites %>% 
  group_by(STATUS) %>% 
  summarise(number=n())

library(flextable)

table.df<-function(df){
  tab<-flextable(df) %>% 
    autofit() %>% 
    theme_vanilla()
  return(tab)
  }

table.df(m.df)

```
\newpage
  
Broken down by team:  

```{r, echo = FALSE, warning= FALSE,message=FALSE}
teams.df<-sites %>% 
  group_by(team,STATUS) %>% 
  summarise(number=n())

tab<-table.df(teams.df)
 tab<-merge_v(tab, j = ~ team)
tab

```
\newpage
  
```{r echo=FALSE,warning=FALSE,message=FALSE}
#dist<-(dist*0.000621371)#this gets you miles between the points
#now get travel time
#dist<-(65/60)*dist#this assumes driving @ 65 mph, so it will be underestimate for short/non highway


#clean up the sites table to get distances right.
sites<-sites %>% 
  group_by(team,date) %>% 
  arrange(team,date,order)

#insert home locations for each trip (this is Albany)
sites.try<-sites %>% 
   group_by(team,date) %>%
   summarise(order = first(order)) %>%
   mutate(SH_LATITUDE = 42.680982, SH_LONGITUDE =-73.696676,SH_SITE_ID="HOME",order = 0) %>% 
   bind_rows(sites, .) %>% 
   arrange(team,date,order)
```

```{r echo=FALSE,warning=FALSE,message=FALSE}

if(params$overnights){
  hotel<-read.csv(here::here(paste("data/hotels/",params$hotel_coords,sep = "")),stringsAsFactors = FALSE)

sites.try.1<-merge(sites.try,hotel,by=c("date","order"),all.x=TRUE)

sites.try.1$lat[is.na(sites.try.1$lat)] <- as.numeric(sites.try.1$SH_LATITUDE)[is.na(sites.try.1$lat)]

sites.try.1$long[is.na(sites.try.1$long)] <- as.numeric(sites.try.1$SH_LONGITUDE)[is.na(sites.try.1$long)]

sites.try.1<-sites.try.1 %>% 
  select(!c(SH_LATITUDE,SH_LONGITUDE)) %>% 
  rename(SH_LATITUDE=lat,
         SH_LONGITUDE=long)

sites.try<-sites.try.1 %>% 
  arrange(team,date,order)

}

new.df<-sites.try %>% 
  select(team,date,order,STATUS,SH_SITE_ID,SH_NAME,SH_DESC,SH_LATITUDE,SH_LONGITUDE,time_to_site,miles_to_site)

#add new row for getting home for the day

home<-new.df %>% 
  group_by(team,date) %>% 
  summarise(order=last(order)) %>% 
  mutate(SH_SITE_ID="HOME_for_the_day",order = max(order)+1) %>% 
   bind_rows(new.df, .) %>% 
   arrange(team,date,order)

file.path.s=file.path(here::here(),
          "RMD/RMD_outputs/")
          
file.save<-paste(file.path.s,"/",params$trip_name,".csv",sep = "")

if(!params$added_drive_times_day_end){
  write.csv(home,file.save,row.names = FALSE)}


#add the times to get home

if(!params$added_drive_times_day_end){
  stop(print(paste("Go to the RMD/RMD outputs folder and add in the times to get home.","filename: ",file.save,sep = "")))

}

```


```{r ft.align="left",warning=FALSE, message=FALSE, echo=FALSE, results= 'asis'}

sum.df<-read.csv(file.save,stringsAsFactors = FALSE)

sum.df<-sum.df %>% 
  group_by(team,date) %>% 
  mutate(sites.num=case_when(
    is.na(SH_NAME)~0,
    TRUE~1
  ))

sum.df.tots<-sum.df %>% 
  group_by(team,date) %>% 
  summarise(n_sites=sum(sites.num),hours=(sum(time_to_site,na.rm = TRUE)/60)+(n_sites*1))

sum.df.tots$hours<-round(sum.df.tots$hours,0)

tab<-table.df(sum.df.tots)
label=paste("Trip Totals (Estimated)")
tab<-flextable::set_caption(tab,label)
tab<-merge_v(tab, j = ~ team + date)
tab<-fit_to_width(tab,max_width = 6)
tab

```


\newpage

## Itineraries

Here are the intineraries.  Shipping Locations will be from `r length(unique(shipping$UPS.Location))` locations.

First, basic trip information:

```{r, echo = FALSE, warning= FALSE,message=FALSE,fig.width=7.5}
knitr::kable(shipping)
```
\newpage

```{r,ft.align="left",warning=FALSE, echo=FALSE, results= 'asis',message=FALSE}
new.df<-sum.df %>% 
  group_by(team,date) %>% 
  mutate(location=paste(SH_LATITUDE,SH_LONGITUDE,sep=","))

dates.l<-unique(new.df$date)

  cat("  \n\n### Team ",params$print_team)
  temp<-new.df[new.df$team %in% params$print_team, ]
  
  for (i in seq_along(dates.l)){
    temp.short<-temp[temp$date %in% dates.l[i], ]
    
    temp.short1<-temp.short %>% 
      select(team,date,order,SH_SITE_ID,SH_NAME,location,STATUS) %>% 
      rename("Team"=team,
             "Date"=date,
             "Order"=order,
             "Site"=SH_SITE_ID,
             "Name"=SH_NAME,
             "Lat/Long"=location,
             "Type"=STATUS)
    
  tab<-table.df(temp.short1)
   label=paste(dates.l[i])
   tab<-flextable::set_caption(tab,label)
  tab<-merge_v(tab, j = ~ Team + Date)
  tab<-fit_to_width(tab,max_width = 7)
  flextable::docx_value(tab)
  cat("<br><br>")
  
  
  temp.short2<-temp.short %>% 
  select(team,date,order,SH_SITE_ID,miles_to_site,time_to_site) %>% 
    mutate(hours=time_to_site/60) %>% 
    mutate(hours=round(hours,1)) %>% 
  rename("Team"=team,
         "Date"=date,
         "Order"=order,
         "Site"=SH_SITE_ID,
         "miles to site"=miles_to_site,
         "Time(minutes)"=time_to_site,
         "Time(hours)"=hours)

  
tab<-table.df(temp.short2)
label=paste("Driving Estimates: ",dates.l[i])
tab<-flextable::set_caption(tab,label)
tab<-merge_v(tab, j = ~ Team + Date)
tab<-fit_to_width(tab,max_width = 7)
flextable::docx_value(tab)
 cat("<br><br>")


temp.short3<-temp.short[temp.short$date %in% dates.l[i], ] %>% 
  select(team,date,order,SH_SITE_ID,SH_DESC) %>% 
  rename("Team"=team,
         "Date"=date,
         "Order"=order,
         "Site"=SH_SITE_ID,
         "DESC"=SH_DESC)


tab<-table.df(temp.short3)
label=paste("Expanded Descriptions: ",dates.l[i])
tab<-flextable::set_caption(tab,label)
tab<-merge_v(tab, j = ~ Team + Date)
tab<-fit_to_width(tab,max_width = 7)
flextable::docx_value(tab)

cat("\n\\newpage\n")

  }


```
