---
title: "Mohawk 2020 Itineraries"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "7/1/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(knitr)
library(flextable)
#insert your file name, number of teams and days here

file.df<-"mohawk_2020.csv"
teams<-4
days<-3
trip_name<-"Mohawk_Screening"
shipping<-data.frame("Location"= c("ALS Courier Service: The ALS address for drop-off is 23A Walker Way, Colonie, The door access code is 6215","Albany,24 Avis Dr, Latham, NY 12110"),"days"=c("Day 2 and 3","Day 1"))
hab_number_start<-155


#read in the raw data
file.path=file.path(here::here(),
          "data",
          file.df)

sites<-read.csv(file.path,stringsAsFactors = FALSE)


#take out the blank ones
sites<-sites %>% 
  subset(!is.na(SH_LATITUDE))

max.sites<-nrow(sites)

```

## Teams

This trip has `r max.sites ` sites to visit total.

There are `r teams ` teams in this sampling event.
Each team will do `r max.sites/teams ` sites over `r days `days. So that's `r (max.sites/teams)/days ` sites per day per team.


1-Gavin/Keleigh   
2-Charlie/Leila  
3- Brian/Meredith    
4-Andrea/Dan   


## Types of sites

This is what the site breakdown looks like for the `r trip_name ` trip:

```{r,message=FALSE,warning=FALSE}
m.df<-sites %>% 
  group_by(STATUS) %>% 
  summarise(number=n())

library(flextable)

table.df<-function(df){
  tab<-flextable(df) %>% 
    autofit() %>% 
    theme_vanilla()
  return(tab)
  }

table.df(m.df)
```
Broken down by team:  
```{r, echo = FALSE, warning= FALSE,message=FALSE}
teams.df<-sites %>% 
  group_by(team,STATUS) %>% 
  summarise(number=n())

tab<-table.df(teams.df)
 tab<-merge_v(tab, j = ~ team)
tab

```


```{r echo=FALSE,warning=FALSE,message=FALSE}

#dist<-(dist*0.000621371)#this gets you miles between the points
#now get travel time
#dist<-(65/60)*dist#this assumes driving @ 65 mph, so it will be underestimate for short/non highway


#clean up the sites table to get distances right.
sites<-sites %>% 
  group_by(team,date) %>% 
  arrange(team,date,order)

#insert home locations for each trip
sites.try<-sites %>% 
   group_by(team,date) %>%
   summarise(order = first(order)) %>%
   mutate(SH_LATITUDE = 42.680982, SH_LONGITUDE =-73.696676,SH_SITE_ID="HOME",order = 0) %>% 
   bind_rows(sites, .) %>% 
   arrange(team,date,order)

#create data frame of the distances
library(geosphere)
dist<- as.data.frame(vapply(2:nrow(sites.try), FUN = function(i) {
    distm(x = c(sites.try$SH_LONGITUDE[i], sites.try$SH_LATITUDE[i]),
          y = c(sites.try$SH_LONGITUDE[i - 1], sites.try$SH_LATITUDE[i - 1]),
          fun = distHaversine)
  },
  FUN.VALUE = NA_real_
  ))

#then change to miles and add time
dist<-dist %>% 
  rename("CTD"=`vapply(2:nrow(sites.try), FUN = function(i) {     distm(x = c(sites.try$SH_LONGITUDE[i], sites.try$SH_LATITUDE[i]), y = c(sites.try$SH_LONGITUDE[i - 1], sites.try$SH_LATITUDE[i - 1]), fun = distHaversine) }, FUN.VALUE = NA_real_)`)
  
dist$miles<-dist$CTD*0.000621371
dist$time.65.mins<-(65/60)*dist$miles

#add extra row to try and bind them #IT WORKED!!
dist<-dist %>% 
   summarise(CTD = last(CTD)) %>%
   mutate(miles=0) %>% 
   bind_rows(.,dist)

new<-merge(dist,sites.try,by="row.names")

new.df<-new %>% 
  select(miles,time.65.mins,STATUS,SH_SITE_ID,SH_DESC,SH_LATITUDE,SH_LONGITUDE,team,date,order,hike)

sites.df<-sites %>% 
  mutate(location=paste(SH_LATITUDE,",",SH_LONGITUDE)) %>% 
  select(team,date,order,SH_SITE_ID,location,Distance.from.Home.Base,Drive_time,total.trip.time,STATUS,hike) %>% 
  group_by(team,date) %>% 
  arrange(team,date,order) %>% 
  mutate(total_num_sites=n())

sites.df$total.trip.time=(0.75*sites.df$total_num_sites)+sites.df$Drive_time
sites.df$date<-as.Date(sites.df$date,"%m/%d/%Y")

new.df$date<-as.Date(new.df$date,"%m/%d/%Y")
new.df<-new.df %>% 
    mutate(location=paste(SH_LATITUDE,",",SH_LONGITUDE))
new.df$time.65.mins<-as.numeric(new.df$time.65.mins)

new.df<-new.df %>% 
  as.data.frame() %>% 
  group_by(team,date) %>% 
  mutate(total_num_sites=n()) %>%
  arrange(team,date,order)


new.df$miles<-ifelse(new.df$SH_SITE_ID=="HOME",0,new.df$miles)
new.df$time.65.mins<-ifelse(new.df$SH_SITE_ID=="HOME",0,new.df$time.65.mins)
new.df$time.65.mins<-ceiling(new.df$time.65.mins)
new.df$miles<-ceiling(new.df$miles)
```

```{r ft.align="left",warning=FALSE, echo=FALSE, results= 'asis'}
sum.df<-new.df %>% 
  select(team,date,time.65.mins,total_num_sites) %>% 
  group_by(team,date) %>% 
  summarise(total.drivng.time.hrs=sum(time.65.mins,na.rm = TRUE)/60,
            sites.num=mean(total_num_sites)-1,
            total.trip=(total.drivng.time.hrs+(sites.num*1.5)))
sum.df$total.drivng.time.hrs<-ceiling(sum.df$total.drivng.time.hrs)
sum.df$total.trip<-ceiling(sum.df$total.trip)

sum.df<-sum.df %>% 
  select(team,date,sites.num,total.trip) %>% 
  rename("Sites (n)"=sites.num,
         "Trip total (hrs)"=total.trip)

tab<-table.df(sum.df)
label=paste("Trip Totals (Estimated)")
tab<-flextable::set_caption(tab,label)
tab<-merge_v(tab, j = ~ team + date)
tab<-fit_to_width(tab,max_width = 6)
flextable::docx_value(tab)

tab
```
\newpage

## Itineraries

Here are the intineraries.  Shipping Locations will be from `r length(shipping)` locations.

First, basic trip information:

```{r, echo = FALSE, warning= FALSE,message=FALSE}
tab<-table.df(shipping)
tab

```

```{r,ft.align="left",warning=FALSE, echo=FALSE, results= 'asis'}

teams.l<-unique(sites.df$team)
sort(teams.l,decreasing = FALSE)
dates.l<-unique(sites.df$date)

for (i in seq_along(teams.l)){
  cat("  \n\n### Team: ",teams.l[i])
  temp<-new.df[new.df$team %in% teams.l[i], ]
  
  for (i in seq_along(dates.l)){
    temp.short<-temp[temp$date %in% dates.l[i], ]
    
    temp.short1<-temp.short %>% 
      select(team,date,order,SH_SITE_ID,location,STATUS,hike) %>% 
      rename("Team"=team,
             "Date"=date,
             "Order"=order,
             "Site"=SH_SITE_ID,
             "Lat/Long"=location,
             "Type"=STATUS,
             "Hike?"=hike)
    
  tab<-table.df(temp.short1)
   label=paste(dates.l[i])
   tab<-flextable::set_caption(tab,label)
  tab<-merge_v(tab, j = ~ Team + Date)
  tab<-fit_to_width(tab,max_width = 6)
  flextable::docx_value(tab)
  cat("  \n")
  
  temp.short2<-temp.short %>% 
  select(team,date,order,SH_SITE_ID,miles,time.65.mins) %>% 
  rename("Team"=team,
         "Date"=date,
         "Order"=order,
         "Site"=SH_SITE_ID,
         "miles to next"=miles,
         "Time(mins)"=time.65.mins)

tab<-table.df(temp.short2)
label=paste("Driving Estimates: ",dates.l[i])
tab<-flextable::set_caption(tab,label)
tab<-merge_v(tab, j = ~ Team + Date)
tab<-fit_to_width(tab,max_width = 6)
flextable::docx_value(tab)
cat("  \n")


temp.short3<-temp.short[temp.short$date %in% dates.l[i], ] %>% 
  select(team,date,order,SH_SITE_ID,SH_DESC) %>% 
  rename("Team"=team,
         "Date"=date,
         "Order"=order,
         "Site"=SH_SITE_ID,
         "DESC"=SH_DESC)

tab<-table.df(temp.short3)
label=paste("Expanded Descriptions: ",dates.l[i])
tab<-flextable::set_caption(tab,label)
tab<-merge_v(tab, j = ~ Team + Date)
tab<-fit_to_width(tab,max_width = 6)
flextable::docx_value(tab)

  
  cat("  \n")
  }}


```

```{r, include=FALSE, message=FALSE,warning=FALSE}
#create the files for processing labels etc.

#first create a folder for the trip
file.path.out=file.path(here::here(),
          "outputs",
          trip_name)

dir.create(trip_name)

#create simple file for quick lookups for excel file #1
short<-new.df %>% 
  select(team,date,order,SH_SITE_ID,SH_LATITUDE,SH_LONGITUDE) %>% 
  filter(SH_SITE_ID!="HOME")

#labels
#bugs
bugs<-new.df %>% 
  select(SH_SITE_ID,date) %>%
  
  rename("SITE_ID"=SH_SITE_ID,
         "DATE"=date) %>% 
  mutate(REP="REP: 1",SURVEY=trip_name)
  
bugs<-bugs[rep(seq_len(nrow(bugs)), each = 2), ]
bugs$DATE<-format(bugs$DATE,"%m/%d/%Y")

#HAB labels
habr<-new.df %>% 
  select(SH_SITE_ID) %>% 
  filter(SH_SITE_ID!="HOME") %>% 
  rename("SiteInfo"=SH_SITE_ID)

habr<-habr[rep(seq_len(nrow(habr)), each = 2), ]

i=nrow(habr)-1
seq.hab=hab_number_start+i


habr<-habr %>% 
  ungroup() %>% 
  mutate(Project="STREAM HABS SAMPLE",SITEID="BAS-LOC-RM:",SampleID=paste0("- _  _  _  _-20-R",seq(hab_number_start,seq.hab,1), sep = ""),Sample_Type=paste("RAW               BOTTLE 1 of ",sequence(rle(as.character(SiteInfo))$lengths)))



```

```{r, include=FALSE,message=FALSE,warning=FALSE}
#write everything to files

# Create a blank workbook
library(openxlsx)
OUT <- createWorkbook()#for lookups
OUT_Chem<-createWorkbook()#for chem labels
OUT2<-createWorkbook()#for all other labels

############################################OUt
# Add some sheets to the workbook

addWorksheet(OUT,"simple_site_info")

# Write the data to the sheets

writeData(OUT, sheet = "simple_site_info", x = short)

############################################OUT2
addWorksheet(OUT2,"BUG_labels")
addWorksheet(OUT2,"HAB_Raw_labels")
addWorksheet(OUT2,"HAB_Scrape_labels")

# Write the data to the sheets

writeData(OUT2, sheet = "BUG_labels", x = bugs)
writeData(OUT2, sheet = "HAB_Raw_labels", x = habr)
writeData(OUT2, sheet = "HAB_Scrape_labels", x = habs)

############################################OUT_Chem
addWorksheet(OUT_Chem,"chem_labels")

# Write the data to the sheets

writeData(OUT_Chem, sheet = "chem_labels", x = chem)


# Reorder worksheets
#worksheetOrder(OUT) <- c(2,1,)

# Export the files
xlfile.path<-file.path(here::here(),
          "outputs",
          trip_name,paste(trip_name,".xlsx",sep = ""))

xlfile.path.label<-file.path(here::here(),
          "outputs",
          trip_name,paste(trip_name,"OTHER_LABELS.xlsx",sep = ""))

xlfile.path.label.chem<-file.path(here::here(),
          "outputs",
          trip_name,paste(trip_name,"_CHEM_LABELS.xlsx",sep = ""))

saveWorkbook(OUT, xlfile.path)
saveWorkbook(OUT2,xlfile.path.label)
saveWorkbook(OUT_Chem,xlfile.path.lable.chem)

```





